---
title: "ROK_data_analysis"
author: "Boglarka Ludmany, Peter Czingraber"
date: "2026-09-16"
output: html_document
---

## Loading packages

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(lmerTest)
library(effectsize)
```

---

## Importing source data

```{r}
source_data = read.csv("arrow_rok_0922.csv")
```

---

## Data cleaning

```{r}
source_data = source_data %>%
  mutate(
    is_header  = participant == "participant",
    session    = cumsum(is_header)
  ) %>%
  filter(!is_header) %>%
  mutate(
    subject_id = paste0("S", str_pad(session, 2, pad = "0"))
  )
```

---

## Building a proper subject code

```{r}
source_data = source_data %>%
  mutate(
    subject_id = paste0("S", str_pad(session, 2, pad = "0"))
  )
```

---

## Demography data

```{r}
demography_data = source_data %>%
  filter(trial_type %in% c("survey-html-form", "survey-multi-choice")) %>%
  select(subject_id, response) %>%
  mutate(
    gender = str_extract(response, '(?<=[Gg]ender":")[^"]+'),
    age = as.numeric(str_extract(response, '(?<="response":")\\d{1,3}(?=")'))
    ) %>%
  select(-response) %>%
  group_by(subject_id) %>%
  summarize(
    age    = age[!is.na(age)][1],
    gender = gender[!is.na(gender)][1],
    .groups = "drop"
  )

demography_data %>%
  summarise(mean_age = mean(age, na.rm = TRUE),
            n_female = sum(gender == "Nő", na.rm = TRUE),
            sd_age = sd(age))
```

---

## Flagging and filtering practice trials 

```{r}
source_data = source_data %>% 
  group_by(subject_id) %>% 
  mutate(
    block_marker = str_detect(stimulus, regex("blokk\\s+vége|end\\s+of\\s+practice\\s+block", ignore_case = TRUE)) %>% 
      coalesce(FALSE),
    block_start  = str_detect(stimulus, regex("Blokk\\s+kezdődik|Block\\s+\\d+\\s+begins", ignore_case = TRUE)) %>% 
      coalesce(FALSE),
    first_trial  = as.integer(lag(block_start, n = 2, default = FALSE)),
    marker_seen  = cummax(block_marker),
    trial_exp    = if_else(marker_seen == 0, "practice", "experimental")
  ) %>% 
  ungroup() 
```

---

## Keeping the necessary variables

```{r}
raw_data = source_data %>% 
  select(subject_id, rt, correct, congruency, trial_exp, trial_index, task, first_trial, time_elapsed) %>% 
  filter(trial_exp == "experimental" & task == "expTrial")
# task == "expTrial" only drops non-trial rows (consent, demographics, etc.);
# trial_exp (from the "blokk vége" marker, computed pre-filter) is what actually separates practice from experimental trials.
```

---

## Source data cleaned, no personal information is retained in the raw data file. This csv is uploaded to github. To reproduce the analysis load the raw_arrow_data.csv

```{r}
write_csv(raw_data,"raw_arrow_data.csv")
```

---

## Importing raw data

```{r}
raw_arrow_data = read.csv("raw_arrow_data.csv")
```

---

## Flagging previous trials

```{r}
raw_arrow_data = raw_arrow_data %>%
  mutate(prev_congruency = lag(congruency, n = 1),
         prev_correct = lag(correct, n = 1),
         correct = ifelse(correct == "true", 1, 0),
         prev_correct = ifelse(prev_correct == "true", 1, 0),
         rt = as.numeric(rt))

# Additional previous-trial variables, needed for the RT-speed analysis
raw_arrow_data = raw_arrow_data %>%
  mutate(prev_rt = lag(rt, n = 1),
         # accuracy of trial N-2; if N-1 is the first trial of a block, N-2 does not exist in the block -> treated as correct
         prev2_correct = if_else(lag(first_trial, n = 1) == 1, 1, lag(correct, n = 2)))
```

---

## Filtering participants with accuracy below 70% 

```{r}
accuracy = raw_arrow_data %>%
  group_by(subject_id) %>%
  summarize(all_accuracy = mean(correct, na.rm = TRUE))

raw_arrow_data = raw_arrow_data %>%
  left_join(accuracy, by = "subject_id") %>%
  filter(all_accuracy > 0.70)
```

---

## Keeping correct trials only, excluding first trials of each block, and participants who did not finish the experiment under 40 minutes (> 2.400.000 ms) 

```{r}
# Trial-level data (all experimental trials of the retained participants); the RT-speed data frame is built from this
trial_level_data = raw_arrow_data %>%
  mutate(time_elapsed = as.numeric(time_elapsed)) %>% 
  group_by(subject_id) %>% 
  mutate(total_time = max(time_elapsed, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(total_time <= 2400000)

filtered_data = trial_level_data %>% 
  filter(correct == 1, prev_correct == 1, rt >= 150, first_trial == 0)
```

---

## Omitting the remaining unnecessary variables

```{r}
processed_data = filtered_data %>%
  select(subject_id, rt, correct, prev_correct, congruency, prev_congruency)
```

---

## Data frame for the RT-speed analysis

```{r}
# One row = trial N together with its previous trial (N-1). Rows are kept if the PREVIOUS trial is valid
# (correct, rt >= 150, and not itself the first trial after an error), regardless of whether trial N is correct:
# the fast/slow tertiles are defined on the previous trials only, so they must not depend on trial N.
# Validity of trial N is kept as a flag (valid_n) and applied only when the RT means are computed.
rt_speed_data = trial_level_data %>% 
  filter(first_trial == 0,
         prev_correct == 1,
         prev2_correct == 1,   
         prev_rt >= 150) %>% 
  mutate(valid_n = as.integer(correct == 1 & rt >= 150)) %>% 
  select(subject_id, rt, correct, valid_n, congruency, prev_congruency, prev_rt)

rt_speed_data %>% 
  group_by(subject_id) %>% 
  summarise(n_pairs = n(), n_valid_n = sum(valid_n))
```
---

## Descriptive statistics and visualisation

```{r}
dstats = function(x, na.omit=FALSE){
  if (na.omit)
  x = x[!is.na(x)]
  min = min(x)
  max = max(x)
  m = mean(x)
  median = median(x)
  n = length(x)
  stds = sd(x)
  skew = 3*(m-median)/stds
  kurt = (length(x) * sum((x - mean(x))^4)) / (sum((x - mean(x))^2)^2) - 3

  
#Return all calculated values to vectors
  return(c(
    min = min,
    max = max,
    mean = m,
    median = median,
    sd = stds,
    skewness = skew,
    kurtosis = kurt
  ))
}
```

---

## Descriptive statistics for aggregated RT values

```{r}
mean_rt_df = processed_data %>% 
  group_by(subject_id) %>% 
  summarise(mean_rt_congruent = mean(rt[congruency == "congruent"]),
            mean_rt_incongruent = mean(rt[congruency == "incongruent"]))

myvars = c("mean_rt_congruent", "mean_rt_incongruent")
sapply(mean_rt_df[myvars], dstats)
```

---

## Density plot

```{r}
ggplot(processed_data, aes(rt)) +
  geom_density() +
  theme_minimal() +
  labs(title = "RT distribution")
```

---

## Violinplots for CE

```{r}
ce_rt = processed_data %>%
  group_by(subject_id, congruency) %>%
  summarise(mean_rt = mean(rt), .groups = "drop")

violin = ggplot(ce_rt, aes(congruency, mean_rt, fill = congruency)) +
  geom_violin(trim = TRUE, bounds = c(0, Inf), width = 0.5) +
  geom_boxplot(width = 0.1, colour = c("black", "white"), outlier.shape = NA) +
  labs(title = "Congruency Effect", x = "Congruency", y = "Mean reaction time (ms)") +
  papaja::theme_apa(base_family = "Times") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("congruent" = "#DAB1DA", "incongruent" = "#341539"))
#ggsave("ce_violin.png", plot = violin, width = 16, height = 9, units = "cm", dpi = 320)
print(violin)
```

---

## Participant level CSE

```{r}
# Appropriate data structure for visualizing the CSE

cse_df = processed_data %>% 
  group_by(subject_id, congruency, prev_congruency) %>% 
  summarise(mean_rt = mean(rt))

cse_descriptive_df = cse_df %>% 
  group_by(congruency, prev_congruency) %>% 
  summarise(N = n(),
            mean = mean(mean_rt),
            sd = sd(mean_rt),
            se = sd/sqrt(N))

wide_df = cse_df %>% 
  pivot_wider(names_from = c(prev_congruency, congruency),
              values_from = mean_rt)

subject_cse = wide_df %>% 
  mutate(CSE = (congruent_incongruent - congruent_congruent) - (incongruent_incongruent - incongruent_congruent))

ggplot(subject_cse, aes(CSE)) +
  geom_density(fill = "#011526", alpha = 0.25) +
  scale_x_continuous(breaks = seq(floor(min(subject_cse$CSE)),
                                  ceiling(max(subject_cse$CSE)),
                                  by = 5)) +
  theme_minimal()

ggplot(subject_cse, aes(CSE)) +
  geom_histogram(fill = "#011526", alpha = 0.25, binwidth = 10) +
  scale_x_continuous(breaks = seq(floor(min(subject_cse$CSE)),
                                  ceiling(max(subject_cse$CSE)),
                                  by = 5)) +
  theme_minimal()
```

---

## CSE plot

```{r}
cse_plot = ggplot(cse_descriptive_df, aes(prev_congruency, mean, colour = congruency, group = congruency)) +
  geom_point(size = 3) +
  geom_path(linewidth = 1.2) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2, linewidth = 1.2) +
                      labs(
                        title = "Congruency-sequence Effect",
                       x = "Previous Congruency",
                       y = "Mean reaction time (ms)",
                       colour = "Congruency") + 
  scale_colour_manual(values = c("#DAB1DA", "#341539")) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "right",
                        plot.title = element_text(hjust = 0.5, face = "bold"),
                        panel.grid = element_blank(),
                        axis.line = element_line(color = "grey", linewidth = 1))
#ggsave("overall_cse_plot.png", plot = cse_plot, width = 16, height = 9, units = "cm", dpi = 320)
print(cse_plot)
```

---

## CSE descriptive

```{r}
myvars = c("CSE")
sapply(subject_cse[myvars], dstats)
```

---

## rmANOVA

```{r}
# Aggregate to one mean RT per participant * condition
rm_data = processed_data %>% 
  group_by(subject_id, congruency, prev_congruency) %>% 
  summarise(mean_rt = mean(rt), .groups = "drop") %>% 
  mutate(congruency = factor(congruency, levels = c("congruent", "incongruent")),
         prev_congruency = factor(prev_congruency, levels = c("congruent", "incongruent")),
         subject_id = factor(subject_id))

# Sum-to-zero contrast coding. congruent = 0.5, incongruent = -0.5
contrasts(rm_data$congruency) = matrix(c(0.5, -0.5), nrow = 2, dimnames = list(NULL, "c_vs_i"))
contrasts(rm_data$prev_congruency) = matrix(c(0.5, -0.5), nrow = 2, dimnames = list(NULL, "c_vs_i"))

# repeated-measures ANOVA
rm_anova = aov(mean_rt ~ congruency * prev_congruency + Error(subject_id / (congruency * prev_congruency)),
               data = rm_data)
summary(rm_anova)
# effect size
eta_squared(rm_anova, partial = TRUE)
```

---

## Post-hoc tests for the main effect of current congruency and the CSE interaction

```{r}
# main effect of current congruency (collapsed across prev_congruency)
main_effect_df = rm_data %>%
  group_by(subject_id, congruency) %>%
  summarise(rt = mean(mean_rt), .groups = "drop") %>%
  pivot_wider(names_from = congruency, values_from = rt)

t_test_CE = t.test(main_effect_df$incongruent, main_effect_df$congruent, paired = TRUE, alternative = "greater")
t_test_CE

# Post-hoc: CSE (interaction), direction + significance
t_test_CSE = t.test(subject_cse$CSE, mu = 0, alternative = "greater")
t_test_CSE
```

---

## Bayesian inference using Dienes's bayes factor function

### Use the t_test_CE object which stores the H1 test parameters, then calculate the BF with robustness regions.

```{r}
t_test_CE
source("dienes_bayes.R")
Bf_h1 = old_Bf(sd = t_test_CE$stderr,
   obtained = t_test_CE$estimate,
   dfdata = t_test_CE$parameter,
   meanoftheory = 0,
   sdtheory = 30,
   dftheory = 10^10,
   tail = 1)
print(Bf_h1)

h1_range = seq(from = 0.5,to = 200,by = 0.5) # Grid starts at 0.5 rather than 0, because old_Bf divides by sdtheory and returns NaN at 0. 
range_test = t(sapply(h1_range, function(sdi) {
  bf_val = old_Bf(
    sd = t_test_CE$stderr,
    obtained = t_test_CE$estimate,
    dfdata = t_test_CE$parameter,
    meanoftheory = 0,
    sdtheory = sdi,
    dftheory = 10^10,
    tail = 1)
  c(sdtheory = sdi, BF = bf_val)
  })) 

colnames(range_test) = c ("sdtheory", "BF")

ev_for_h1 = subset(data.frame(range_test), BF > 3)
low_threshold_mcm = min(ev_for_h1$sdtheory)
high_threshold_mcm = max(ev_for_h1$sdtheory)
print(range_test)
```

---

### Use the t_test_CSE object which stores the H2 test parameters, then calculate the BF with robustness regions.

```{r}
t_test_CSE
Bf_h2 = old_Bf(sd = t_test_CSE$stderr,
   obtained = t_test_CSE$estimate,
   dfdata = t_test_CSE$parameter,
   meanoftheory = 0,
   sdtheory = 30,
   dftheory = 10^10,
   tail = 1)
print(Bf_h2)

h2_range = seq(from = 0.5, to = 200, by = 0.5) 
range_test = t(sapply(h2_range, function(sdi) {
  bf_val = old_Bf(
    sd = t_test_CSE$stderr,
    obtained = t_test_CSE$estimate,
    dfdata = t_test_CSE$parameter,
    meanoftheory = 0,
    sdtheory = sdi,
    dftheory = 10^10,
    tail = 1)
  c(sdtheory = sdi, BF = bf_val)
  })) 

colnames(range_test) = c ("sdtheory", "BF")

ev_for_h2 = subset(data.frame(range_test), BF > 3)
low_threshold_mcm = min(ev_for_h2$sdtheory)
high_threshold_mcm = max(ev_for_h2$sdtheory)
print(range_test)
```

---

## RT-speed analysis

### Fast / slow tertiles of the previous trial's RT

```{r}
# Tertiles are computed separately within previous-congruent and previous-incongruent trials of every participant
# (Weissman et al., 2026), so that previous conflict is varied while previous congruency is held constant.
assign_speed = function(df, by) {
  df %>% 
    group_by(across(all_of(by))) %>% 
    mutate(q_lo = quantile(prev_rt, 1/3),
           q_hi = quantile(prev_rt, 2/3),
           prev_speed = case_when(prev_rt <= q_lo ~ "fast",
                                  prev_rt >= q_hi ~ "slow",
                                  TRUE ~ "middle")) %>% 
    ungroup()
}

speed_data = assign_speed(rt_speed_data, by = c("subject_id", "prev_congruency"))

speed_cells = speed_data %>% 
  filter(valid_n == 1, prev_speed != "middle") %>% 
  group_by(subject_id, prev_congruency, prev_speed, congruency) %>% 
  summarise(mean_rt = mean(rt), mean_prev_rt = mean(prev_rt), n = n(), .groups = "drop")

```

---

### Manipulation check: do the fast and slow tertiles differ in previous-trial RT?

```{r}
speed_cells %>% 
  group_by(subject_id, prev_congruency, prev_speed) %>% 
  summarise(prev_rt = mean(mean_prev_rt), .groups = "drop") %>% 
  pivot_wider(names_from = prev_speed, values_from = prev_rt) %>% 
  group_by(prev_congruency) %>% 
  summarise(mean_fast = mean(fast), mean_slow = mean(slow),
            t = unname(t.test(slow, fast, paired = TRUE)$statistic),
            p = t.test(slow, fast, paired = TRUE)$p.value)
```

---

### Modulation of the congruency effect (one value per participant and previous congruency)

```{r}
# modulation = CE after fast previous trials - CE after slow previous trials
# Positive values = smaller congruency effect after slow (high-conflict) trials = what the conflict account predicts
get_modulation = function(cells, strata) {
  cells %>% 
    pivot_wider(id_cols = c(subject_id, all_of(strata), prev_speed),
                names_from = congruency, values_from = mean_rt) %>% 
    mutate(CE = incongruent - congruent) %>% 
    pivot_wider(id_cols = c(subject_id, all_of(strata)),
                names_from = prev_speed, values_from = CE, names_prefix = "CE_") %>% 
    mutate(modulation = CE_fast - CE_slow) %>% 
    filter(!is.na(modulation))
}

speed_modulation = get_modulation(speed_cells, strata = "prev_congruency")

speed_modulation %>% 
  group_by(prev_congruency) %>% 
  summarise(across(c(CE_fast, CE_slow, modulation), mean))
```

---

## TOST and Bayes factor on the modulation

### Setting up the two modulation vectors

```{r}
mod_congruent = speed_modulation %>% 
  filter(prev_congruency == "congruent") %>% pull(modulation)
mod_incongruent = speed_modulation %>%
  filter(prev_congruency == "incongruent") %>% pull(modulation)
```

---

### TOST

```{r}
sesoi = 5

# previous trial congruent
tost_c_lower = t.test(mod_congruent, mu = -sesoi, alternative = "greater")   # H0: modulation <= -5
tost_c_upper = t.test(mod_congruent, mu = sesoi, alternative = "less")       # H0: modulation >= +5

# previous trial incongruent
tost_i_lower = t.test(mod_incongruent, mu = -sesoi, alternative = "greater")
tost_i_upper = t.test(mod_incongruent, mu = sesoi, alternative = "less")

tibble(prev_congruency = c("congruent", "incongruent"),
       p_lower = c(tost_c_lower$p.value, tost_i_lower$p.value),
       p_upper = c(tost_c_upper$p.value, tost_i_upper$p.value)) %>% 
  mutate(p_TOST = pmax(p_lower, p_upper),   # equivalence needs both tests significant
         equivalent = p_TOST < 0.05)
```

---

### BF, previous congruent

```{r}
t_test_speed_cong = t.test(mod_congruent, mu = 0, alternative = "greater")

Bf_H3_cong = old_Bf(sd = t_test_speed_cong$stderr,
                    obtained = t_test_speed_cong$estimate,
                    dfdata = t_test_speed_cong$parameter,
                    meanoftheory = 0,
                    sdtheory = 30,
                    dftheory = 10^10,
                    tail = 1)
print(Bf_H3_cong) 
speed_range = seq(from = 0.5, to = 200, by = 0.5)
range_test_c = t(sapply(speed_range, function(sdi) {
  bf_val = old_Bf(sd = t_test_speed_cong$stderr,
                  obtained = t_test_speed_cong$estimate,
                  dfdata = t_test_speed_cong$parameter,
                  meanoftheory = 0,
                  sdtheory = sdi,
                  dftheory = 10^10,
                  tail = 1)
  c(sdtheory = sdi, BF = bf_val)
}))
colnames(range_test_c) = c("sdtheory", "BF")
range_test_c = data.frame(range_test_c)

ev_for_h3_cong = subset(data.frame(range_test), BF > 3) # BF > 3 indicates evidence for the conflict-monitoring account
low_threshold_mcm = min(ev_for_h3_cong$sdtheory)
high_threshold_mcm = max(ev_for_h3_cong$sdtheory)
print(range_test)
```

---

### BF, previous incongruent

```{r}
t_test_speed_incong = t.test(mod_incongruent, mu = 0, alternative = "greater")

Bf_H3_incong = old_Bf(sd = t_test_speed_incong$stderr,
                    obtained = t_test_speed_incong$estimate,
                    dfdata = t_test_speed_incong$parameter,
                    meanoftheory = 0,
                    sdtheory = 30,
                    dftheory = 10^10,
                    tail = 1)
print(Bf_H3_incong)

range_test_i = t(sapply(speed_range, function(sdi) {
  bf_val = old_Bf(sd = t_test_speed_incong$stderr,
                  obtained = t_test_speed_incong$estimate,
                  dfdata = t_test_speed_incong$parameter,
                  meanoftheory = 0,
                  sdtheory = sdi,
                  dftheory = 10^10,
                  tail = 1)
  c(sdtheory = sdi, BF = bf_val)
}))
colnames(range_test_i) = c("sdtheory", "BF")
range_test_i = data.frame(range_test_i)

ev_for_h3_incong = subset(data.frame(range_test), BF > 3) # BF > 3 indicates evidence for the conflict-monitoring account. In the case of both congruency type, BF needs to be > 3 to conclude evidence for the conflict monitoring account
low_threshold_mcm = min(ev_for_h3_incong$sdtheory)
high_threshold_mcm = max(ev_for_h3_incong$sdtheory)
print(range_test)
```

### Plots

```{r}
speed_plot_df = speed_cells %>% 
  group_by(prev_congruency, prev_speed, congruency) %>% 
  summarise(mean = mean(mean_rt), se = sd(mean_rt) / sqrt(n()), .groups = "drop") %>% 
  mutate(prev_speed = factor(prev_speed, levels = c("fast", "slow")))

ggplot(speed_plot_df, aes(prev_speed, mean, colour = congruency, group = congruency)) +
  geom_point(size = 3) +
  geom_path(linewidth = 1.2) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2, linewidth = 1.2) +
  facet_wrap(~ prev_congruency, labeller = label_both) +
  labs(title = "RT-speed analysis", x = "Previous-trial RT tertile", y = "Mean reaction time (ms)", colour = "Congruency") +
  scale_colour_manual(values = c("#DAB1DA", "#341539")) +
  theme_minimal(base_size = 14)

ggplot(speed_modulation, aes(prev_congruency, modulation)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = -5, ymax = 5, alpha = 0.15) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_jitter(width = 0.08, height = 0, alpha = 0.6) +
  stat_summary(fun.data = mean_cl_normal, fun.args = list(conf.int = 0.90), colour = "#341539") +
  labs(x = "Previous congruency", y = "CE(fast) - CE(slow) (ms)",
       subtitle = "Grey band = equivalence bounds (+/- 5 ms); mean with 90% CI") +
  theme_minimal(base_size = 14)
```

---

## How many participants / trials did we exclude? (standard CSE analysis)

```{r}
raw_arrow_rows = nrow(raw_arrow_data)

filtered_invalid = raw_arrow_data %>%
  mutate(time_elapsed = as.numeric(time_elapsed)) %>% 
  group_by(subject_id) %>% 
  mutate(total_time = max(time_elapsed, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(total_time >= 2400000 | correct == 0 | prev_correct == 0 | rt <= 150 | first_trial != 0) %>%
  select(subject_id, rt, correct, congruency, prev_congruency, prev_rt)

filtered_invalid_rows = nrow(filtered_invalid)

filtered_invalid_perc = (filtered_invalid_rows / raw_arrow_rows) * 100
filtered_invalid_rows
filtered_invalid_perc
```


```{r}
# Too slow
slow_trials = raw_arrow_data %>% 
  mutate(time_elapsed = as.numeric(time_elapsed)) %>% 
  group_by(subject_id) %>% 
  mutate(total_time = max(time_elapsed, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(total_time >= 2400000)

n_slow = n_distinct(slow_trials$subject_id)

# Inaccurate
inaccurate = accuracy %>% 
  filter(all_accuracy < 0.70)
n_inaccurate = n_distinct(inaccurate$subject_id)

n_slow
n_inaccurate
```

---

### How many trials did we exclude before the RT-matching analysis?

```{r}
speed_final = speed_data %>% 
  filter(valid_n == 1, prev_speed != "middle")
```

```{r}
raw_arrow_data_orig = read.csv("raw_arrow_data.csv")

n_trials_total     = nrow(raw_arrow_data_orig)
n_trials_final     = nrow(speed_final)
n_trials_excluded  = n_trials_total - n_trials_final
pct_trials_excluded = n_trials_excluded / n_trials_total * 100

cat(
  "Total trials:   ", n_trials_total, "\n",
  "Final trials:   ", n_trials_final, "\n",
  "Excluded trials:", n_trials_excluded, "\n",
  "Pct excluded:   ", round(pct_trials_excluded, 2), "%\n",
  sep = ""
)
```






