---
title: "ROK_data_analysis"
author: "Peter Czingraber"
date: "2026-09-16"
output: html_document
---

## Loading packages

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(lmerTest)
```

---

## Importing raw data

```{r}
raw_pilot_data = read.csv("inlab_pilot.csv")
```

---

## Data cleaning

```{r}
demography_data = raw_pilot_data %>%
  filter(trial_type %in% c("survey-html-form", "survey-multi-choice")) %>%
  select(participant, response) %>%
  mutate(
    gender = str_extract(response, '(?<=[Gg]ender":")[^"]+'),
    age = as.numeric(str_extract(response, '(?<="response":")\\d{1,3}(?=")'))
    ) %>%
  select(-response) %>%
  group_by(participant) %>%
  summarize(
    age    = age[!is.na(age)][1],
    gender = gender[!is.na(gender)][1],
    .groups = "drop"
  )

demography_data %>%
  summarise(mean_age = mean(age, na.rm = TRUE),
            n_female = sum(gender == "Nő", na.rm = TRUE))
```

---

## Flagging and filtering practice trials 

```{r}
raw_pilot_data = raw_pilot_data %>% 
  group_by(participant) %>% 
  mutate(
    block_marker = str_detect(stimulus, regex("blokk\\s+vége", ignore_case = TRUE)) %>% 
      coalesce(FALSE),
    block_start  = str_detect(stimulus, regex("Blokk\\s+kezdődik", ignore_case = TRUE)) %>% 
      coalesce(FALSE),
    first_trial  = as.integer(lag(block_start, n = 2, default = FALSE)),
    marker_seen  = cummax(block_marker),
    trial_exp    = if_else(marker_seen == 0, "practice", "experimental")
  ) %>% 
  ungroup() 
```

---

## Keeping the necessary variables

```{r}
raw_pilot_data = raw_pilot_data %>% 
  select(participant, rt, correct, congruency, trial_exp, trial_index, task, first_trial, time_elapsed) %>% 
  filter(trial_exp == "experimental" & task == "expTrial")
# task == "expTrial" only drops non-trial rows (consent, demographics, etc.);
# trial_exp (from the "blokk vége" marker, computed pre-filter) is what actually separates practice from experimental trials.
```

---

## Flagging previous trials

```{r}
raw_pilot_data = raw_pilot_data %>%
  mutate(prev_congruency = lag(congruency, n = 1),
         prev_correct = lag(correct, n = 1),
         correct = ifelse(correct == "true", 1, 0),
         prev_correct = ifelse(prev_correct == "true", 1, 0),
         rt = as.numeric(rt))
```

---

## Filtering participants with accuracy below 60% 

```{r}
accuracy = raw_pilot_data %>%
  group_by(participant) %>%
  summarize(all_accuracy = mean(correct, na.rm = TRUE))

raw_pilot_data = raw_pilot_data %>%
  left_join(accuracy, by = "participant") %>%
  filter(all_accuracy > 0.70)
```

---

## Keeping correct trials only, excluding first trials of each block, and participants who did not finish the experiment under 40 minutes (> 2.400.000 ms) 

```{r}
filtered_pilot_data = raw_pilot_data %>%
  mutate(time_elapsed = as.numeric(time_elapsed)) %>% 
  group_by(participant) %>% 
  mutate(total_time = max(time_elapsed, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(total_time <= 2400000) %>% 
  filter(correct == 1, prev_correct == 1, rt >= 150, first_trial == 0)
```

---

## Omitting the remaining unnecessary variables


```{r}
processed_pilot_data = filtered_pilot_data %>%
  select(participant, rt, correct, prev_correct, congruency, prev_congruency)
```

---

## Descriptive statistics and visualisation

```{r}
dstats = function(x, na.omit=FALSE){
  if (na.omit)
  x = x[!is.na(x)]
  min = min(x)
  max = max(x)
  m = mean(x)
  median = median(x)
  n = length(x)
  stds = sd(x)
  skew = 3*(m-median)/stds
  kurt = (length(x) * sum((x - mean(x))^4)) / (sum((x - mean(x))^2)^2) - 3

  
#Return all calculated values to vectors
  return(c(
    min = min,
    max = max,
    mean = m,
    median = median,
    sd = stds,
    skewness = skew,
    kurtosis = kurt
  ))
}
```

---

## Descriptive statistics for aggregated RT values

```{r}
mean_rt_df = processed_pilot_data %>% 
  group_by(participant) %>% 
  summarise(mean_rt_congruent = mean(rt[congruency == "congruent"]),
            mean_rt_incongruent = mean(rt[congruency == "incongruent"]))

myvars = c("mean_rt_congruent", "mean_rt_incongruent")
sapply(mean_rt_df[myvars], dstats)
```

---

## Density plot

```{r}
ggplot(processed_pilot_data, aes(rt)) +
  geom_density() +
  theme_minimal() +
  labs(title = "RT distribution")
```

---

## Violinplots for CE

```{r}
ce_rt = processed_pilot_data %>%
  group_by(participant, congruency) %>%
  summarise(mean_rt = mean(rt), .groups = "drop")

violin = ggplot(ce_rt, aes(congruency, mean_rt, fill = congruency)) +
  geom_violin(trim = TRUE, bounds = c(0, Inf), width = 0.5) +
  geom_boxplot(width = 0.1, colour = c("black", "white"), outlier.shape = NA) +
  labs(title = "Congruency Effect", x = "Congruency", y = "Mean reaction time (ms)") +
  papaja::theme_apa(base_family = "Times") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("congruent" = "#DAB1DA", "incongruent" = "#341539"))
#ggsave("ce_violin.png", plot = violin, width = 16, height = 9, units = "cm", dpi = 320)
print(violin)
```

---

## Participant level CSE

```{r}
# Appropriate data structure for visualizing the CSE

cse_df = processed_pilot_data %>% 
  group_by(participant, congruency, prev_congruency) %>% 
  summarise(mean_rt = mean(rt))

cse_descriptive_df = cse_df %>% 
  group_by(congruency, prev_congruency) %>% 
  summarise(N = n(),
            mean = mean(mean_rt),
            sd = sd(mean_rt),
            se = sd/sqrt(N))

wide_df = cse_df %>% 
  pivot_wider(names_from = c(prev_congruency, congruency),
              values_from = mean_rt)

subject_cse = wide_df %>% 
  mutate(CSE = (congruent_incongruent - congruent_congruent) - (incongruent_incongruent - incongruent_congruent))

ggplot(subject_cse, aes(CSE)) +
  geom_density(fill = "#011526", alpha = 0.25) +
  scale_x_continuous(breaks = seq(floor(min(subject_cse$CSE)),
                                  ceiling(max(subject_cse$CSE)),
                                  by = 5)) +
  theme_minimal()

ggplot(subject_cse, aes(CSE)) +
  geom_histogram(fill = "#011526", alpha = 0.25, binwidth = 10) +
  scale_x_continuous(breaks = seq(floor(min(subject_cse$CSE)),
                                  ceiling(max(subject_cse$CSE)),
                                  by = 5)) +
  theme_minimal()
```

---

## CSE plot

```{r}
cse_plot = ggplot(cse_descriptive_df, aes(prev_congruency, mean, colour = congruency, group = congruency)) +
  geom_point(size = 3) +
  geom_path(linewidth = 1.2) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2, linewidth = 1.2) +
                      labs(
                        title = "Congruency-sequence Effect",
                       x = "Previous Congruency",
                       y = "Mean reaction time (ms)",
                       colour = "Congruency") + 
  scale_colour_manual(values = c("#DAB1DA", "#341539")) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "right",
                        plot.title = element_text(hjust = 0.5, face = "bold"),
                        panel.grid = element_blank(),
                        axis.line = element_line(color = "grey", linewidth = 1))
#ggsave("overall_cse_plot.png", plot = cse_plot, width = 16, height = 9, units = "cm", dpi = 320)
print(cse_plot)
```

---

## CSE descriptive

```{r}
myvars = c("CSE")
sapply(subject_cse[myvars], dstats)
```

---

## rmANOVA

```{r}
# Aggregate to one mean RT per participant * condition
rm_data = processed_pilot_data %>% 
  group_by(participant, congruency, prev_congruency) %>% 
  summarise(mean_rt = mean(rt), .groups = "drop") %>% 
  mutate(congruency = factor(congruency, levels = c("congruent", "incongruent")),
         prev_congruency = factor(prev_congruency, levels = c("congruent", "incongruent")),
         participant = factor(participant))

# Sum-to-zero contrast coding. congruent = 0.5, incongruent = -0.5
contrasts(rm_data$congruency) = matrix(c(0.5, -0.5), nrow = 2, dimnames = list(NULL, "c_vs_i"))
contrasts(rm_data$prev_congruency) = matrix(c(0.5, -0.5), nrow = 2, dimnames = list(NULL, "c_vs_i"))

# repeated-measures ANOVA
rm_anova = aov(mean_rt ~ congruency * prev_congruency + Error(participant / (congruency * prev_congruency)),
               data = rm_data)
summary(rm_anova)
```

---

## Post-hoc tests for the main effect of current congruency and the CSE interaction

```{r}
# main effect of current congruency (collapsed across prev_congruency)
main_effect_df = rm_data %>%
  group_by(participant, congruency) %>%
  summarise(rt = mean(mean_rt), .groups = "drop") %>%
  pivot_wider(names_from = congruency, values_from = rt)

t_test_CE = t.test(main_effect_df$incongruent, main_effect_df$congruent, paired = TRUE, alternative = "greater")
t_test_CE

# Post-hoc: CSE (interaction), direction + significance
t_test_CSE = t.test(subject_cse$CSE, mu = 0, alternative = "greater")
t_test_CSE
```

---

## Bayesian inference using Dienes's bayes factor function

### Use the t_test_CE object which stores the H1 test parameters, then calculate the BF with robustness regions.

```{r}
t_test_CE
source("dienes_bayes.R")
Bf_h1 = old_Bf(sd = t_test_CE$stderr,
   obtained = t_test_CE$estimate,
   dfdata = t_test_CE$parameter,
   meanoftheory = 0,
   sdtheory = 30,
   dftheory = 10^10,
   tail = 1)
print(Bf_h1)

h1_range = seq(from = 0.5,to = 200,by = 0.5) # Grid starts at 0.5 rather than 0, because old_Bf divides by sdtheory and returns NaN at 0. 
range_test = t(sapply(h1_range, function(sdi) {
  bf_val = old_Bf(
    sd = t_test_CE$stderr,
    obtained = t_test_CE$estimate,
    dfdata = t_test_CE$parameter,
    meanoftheory = 0,
    sdtheory = sdi,
    dftheory = 10^10,
    tail = 1)
  c(sdtheory = sdi, BF = bf_val)
  })) 

colnames(range_test) = c ("sdtheory", "BF")

ev_for_h1 = subset(data.frame(range_test), BF > 3)
low_threshold_mcm = min(ev_for_h1$sdtheory)
high_threshold_mcm = max(ev_for_h1$sdtheory)
print(range_test)
```

---

### Use the t_test_CSE object which stores the H2 test parameters, then calculate the BF with robustness regions.

```{r}
t_test_CSE
Bf_h2 = old_Bf(sd = t_test_CSE$stderr,
   obtained = t_test_CSE$estimate,
   dfdata = t_test_CSE$parameter,
   meanoftheory = 0,
   sdtheory = 30,
   dftheory = 10^10,
   tail = 1)
print(Bf_h2)

h2_range = seq(from = 0.5,to = 200,by = 0.5) 
range_test = t(sapply(h2_range, function(sdi) {
  bf_val = old_Bf(
    sd = t_test_CSE$stderr,
    obtained = t_test_CSE$estimate,
    dfdata = t_test_CSE$parameter,
    meanoftheory = 0,
    sdtheory = sdi,
    dftheory = 10^10,
    tail = 1)
  c(sdtheory = sdi, BF = bf_val)
  })) 

colnames(range_test) = c ("sdtheory", "BF")

ev_for_h2 = subset(data.frame(range_test), BF > 3)
low_threshold_mcm = min(ev_for_h2$sdtheory)
high_threshold_mcm = max(ev_for_h2$sdtheory)
print(range_test)
```























