---
title: "weissman-integrated"
author: "Boglarka Ludmany"
date: "2026-09-20"
output: html_document
---

# ===================================================
# Only for explanation purposes

# Data filtering: 3 sd from (participant-level) mean RT 

```{r}
sd_summary <- processed_data %>%
  group_by(participant_id, cong, prev_cong) %>%
  summarise(participant_mean = mean(rt), 
            participant_sd = sd(rt))

processed_data <- processed_data %>%
  left_join(., participant_summary, by = c("participant_id", "congruency_type", "previous_congruency_type"))
 
processed_data <- processed_data %>%
  filter(abs(participant_sd) < 3)
```

## using a function: 
```{r}
sd_filter <- function(data) {
  sd_summary <- data %>% 
    group_group_by(participant_id, cong, prev_cong) %>%
  summarise(participant_mean = mean(rt), 
            participant_sd = sd(rt))
  
  sd_added <- data %>% 
    left_join(., participant_summary, by = c("participant_id", "cong", "prev_cong"))
  
  sd_trimmed <- sd_added %>% 
    filter(abs(participant_sd) < 3)
}
```

# Column roles actually used by the MATLAB script (1-indexed, matching R):
```{r}
#   V1  = Run label ("practice", 1-8)      <- used to strip practice trials
#   V2  = Trial number (1-96)               <- used to flag Warmup (1-4) vs Real
#   V5  = Congruency of trial N             ("Congruent"/"Incongruent")
#   V6  = Congruency of trial N-1
#   V7  = Congruency of trial N-2
#   V12 = RT
#   V13 = Accuracy of trial N               ("Correct"/"Error"/"Omission")
#   V14 = Accuracy of trial N-1
#   V15 = Accuracy of trial N-2
# (V3, V4, V8-V11, V16 exist in the file but are never referenced by the original script, so they're read in but otherwise unused here too.)
```

# ---- Column position constants (see note above) ----------------------------
```{r}
COL_RUN         <- 1
COL_TRIAL       <- 2
COL_CURR_CONG   <- 5
COL_PREV_CONG   <- 6
COL_PREV_CONG2  <- 7
COL_RT          <- 12
COL_ACC         <- 13
COL_PREV_ACC    <- 14
COL_PREV_ACC2   <- 15
```

# ---- Helper: pull the subset of rows matching a congruency-sequence pattern
# cur/prev/prev2 are "Congruent"/"Incongruent" for trials N, N-1, N-2.
# acc_cols is a named list of which accuracy columns must equal "Correct",
# e.g. list(curr = TRUE, prev = TRUE, prev2 = TRUE) or list(prev = TRUE, prev2 = TRUE).

```{r}
get_condition <- function(df, cur, prev, prev2,
                           require_curr_correct = FALSE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE) # returns correct rt trials
  {
  keep <- df[[COL_CURR_CONG]]  == cur  & # col curr cong = 5 -> output: a vector -> t/f
          df[[COL_PREV_CONG]]  == prev & # col number: 6
          df[[COL_PREV_CONG2]] == prev2 & # col number: 7
          df$Warmup == "Real" # drops practice and warm-up trials
  # after this: keep is a logical vector with one entry per row of df (true: matches the requested congurency pattern, and is a real trial)
  
  if (require_curr_correct)  keep <- keep & df[[COL_ACC]]       == "Correct"
  # runs the line only when the flag is true -> then builds a t/f vector for col13 
  
  if (require_prev_correct)  keep <- keep & df[[COL_PREV_ACC]]  == "Correct"
  if (require_prev2_correct) keep <- keep & df[[COL_PREV_ACC2]] == "Correct"
  # same but with diff cols
  
  df[keep, , drop = FALSE] 
}

# so basically: 
get_condition_tidyverse <- function(df, cur, prev, prev2, # Those parameters exist because the function picks out one cell per call
                          require_curr_correct  = FALSE,
                          require_prev_correct  = TRUE,
                          require_prev2_correct = TRUE) {
  df %>%
    filter(
      Curr_Cong  == cur,
      Prev_Cong  == prev,
      Prev_Cong2 == prev2,
      Warmup     == "Real",
      !require_curr_correct  | Acc       == "Correct",
      !require_prev_correct  | Prev_Acc  == "Correct",
      !require_prev2_correct | Prev_Acc2 == "Correct"
    )
}

# for example: 
# RT analysis: correct trials only on N
get_condition(df, "Incongruent", "Congruent", "Congruent", require_curr_correct = TRUE) %>%
  summarise(mean_rt = mean(RT))

# error-rate analysis: keep errors on N
get_condition(df, "Incongruent", "Congruent", "Congruent") %>%
  summarise(error_rate = mean(Acc == "Incorrect"))

# in other words: 
# give the positional columns readable names once, at the top
df <- df %>%
  rename(Curr_Cong  = 5,
         Prev_Cong  = 6,
         Prev_Cong2 = 7,
         RT         = 12,
         Acc        = 13,
         Prev_Acc   = 14,
         Prev_Acc2  = 15)

# RT analysis: correct trials on N, N-1 and N-2
rt_cells <- df %>%
  filter(Warmup == "Real",
         Acc == "Correct",
         Prev_Acc == "Correct",
         Prev_Acc2 == "Correct") %>%
  group_by(Subject, Prev_Cong2, Prev_Cong, Curr_Cong) %>%
  summarise(mean_rt = mean(RT), n_trials = n(), .groups = "drop")
```


# Pre-final step: process one subject's file (then, next step: loop all over every subject's file)
```{r}
process_subject_file <- function(file_name) {

  sub_num <- as.numeric(regmatches(
    file_name,
    regexpr("(?<=Prime_Digit_Flanker_Subject_)[0-9]+", file_name, perl = TRUE)
  )) # TODO: TIDYVERS EQUIVALENT: sub_num <- stringr::str_extract(file_name, "(?<=Subject_)\\d+") %>% as.numeric()


  # Read as raw text/character columns, no header, tab-delimited
  raw <- read.delim(file_name, header = FALSE, sep = "\t",
                     colClasses = "character", quote = "\"",
                     stringsAsFactors = FALSE)

# ---- Strip practice trials --------------------------------------------
  practice_rows <- which(raw[[COL_RUN]] == "practice")
  first_test_trial <- max(practice_rows) + 1
  data <- raw[first_test_trial:nrow(raw), , drop = FALSE]

# ---- Flag Warmup (trials 1-4 of each block) vs Real (5-68) -------------
  data$Warmup <- ifelse(data[[COL_TRIAL]] %in% c("1", "2", "3", "4"),
                         "Warmup", "Real") 

  # Numeric RT column
  data$RT <- suppressWarnings(as.numeric(data[[COL_RT]]))

  # =========================================================================
  # I. Congruency sequence effects in RT (correct trials preceded by
  #    two correct trials)
  # =========================================================================
  # "_rep" = trial N-2 was Incongruent; "_alt" = trial N-2 was Congruent
  cond_specs_I <- list(
    iI_rep = c("Incongruent", "Incongruent", "Incongruent"),
    cI_rep = c("Incongruent", "Congruent",   "Incongruent"),
    cC_rep = c("Congruent",   "Congruent",   "Incongruent"),
    iC_rep = c("Congruent",   "Incongruent", "Incongruent"),
    iI_alt = c("Incongruent", "Incongruent", "Congruent"),
    cI_alt = c("Incongruent", "Congruent",   "Congruent"),
    cC_alt = c("Congruent",   "Congruent",   "Congruent"),
    iC_alt = c("Congruent",   "Incongruent", "Congruent")
  ) 

  rt_trimmed <- list()
  n_outliers <- list()

  for (nm in names(cond_specs_I)) {
    spec <- cond_specs_I[[nm]]
    sub  <- get_condition(data, spec[1], spec[2], spec[3],
                           require_curr_correct = TRUE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE) # keeps the real trials with that congruency pattern where trials n, n-1, n-2 are all correct 
    tr <- trim_3sd(sub$RT) 
    rt_trimmed[[nm]] <- tr$trimmed
    n_outliers[[nm]] <- tr$n_outliers
  }

  mean_rt <- vapply(rt_trimmed, function(x) mean(x, na.rm = TRUE), numeric(1))
  # gives one mean per cell: a named vector of 8 numbers

  # Combined SDs across matched "rep"/"alt" x I/C groupings -> SDs calculated by condition 
  std_I_rep <- stats::sd(c(rt_trimmed$iI_rep, rt_trimmed$cI_rep), na.rm = TRUE)
  std_C_rep <- stats::sd(c(rt_trimmed$cC_rep, rt_trimmed$iC_rep), na.rm = TRUE)
  std_I_alt <- stats::sd(c(rt_trimmed$iI_alt, rt_trimmed$cI_alt), na.rm = TRUE)
  std_C_alt <- stats::sd(c(rt_trimmed$cC_alt, rt_trimmed$iC_alt), na.rm = TRUE) 

  total_num_outliers   <- sum(unlist(n_outliers)) 
  total_percent_outliers <- total_num_outliers / nrow(data)

  # =========================================================================
  # II. Congruency sequence effects in accuracy -- NOT RELEVANT FOR US
  #     (Method B in the original script: exclude omissions, then exclude
  #      RT outliers > 3 SD, then compute percent correct on what remains.
  #      This is the version whose numbers are actually written to file --
  #      the MATLAB "Method A", which skips the omission/outlier exclusion,
  #      is computed there too but never written out, so it's omitted here.)
  # =========================================================================
  pc <- list()

  for (nm in names(cond_specs_I)) {
    spec <- cond_specs_I[[nm]]
    sub  <- get_condition(data, spec[1], spec[2], spec[3],
                           require_curr_correct = FALSE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE)

    # Exclude omissions
    sub <- sub[sub[[COL_ACC]] != "Omission", , drop = FALSE]

    # Exclude RT outliers > 3 SD from that condition's own mean
    m <- mean(sub$RT, na.rm = TRUE)
    s <- stats::sd(sub$RT, na.rm = TRUE)
    kept <- sub[!is.na(sub$RT) & sub$RT >= (m - 3 * s) & sub$RT <= (m + 3 * s), ,
                drop = FALSE]

    pc[[nm]] <- if (nro[118;1:3uw(kept) > 0) mean(kept[[COL_ACC]] == "Correct") else NA_real_
  }

  # =========================================================================
  # III. Overall accuracy (Method C): correct trials / all test trials --> so no SD trimming? 
  # =========================================================================
  overall_accuracy <- mean(data[[COL_ACC]] == "Correct")

  # ---- Assemble this subject's output row (same column order as MATLAB) --
  data.frame(
    SubNum   = sub_num,
    ccC_RT   = mean_rt["cC_alt"],
    ccI_RT   = mean_rt["cI_alt"],
    ciC_RT   = mean_rt["iC_alt"],
    ciI_RT   = mean_rt["iI_alt"],
    icC_RT   = mean_rt["cC_rep"],
    icI_RT   = mean_rt["cI_rep"],
    iiC_RT   = mean_rt["iC_rep"],
    iiI_RT   = mean_rt["iI_rep"],
    ccC_PC   = pc$cC_alt,
    ccI_PC   = pc$cI_alt,
    ciC_PC   = pc$iC_alt,
    ciI_PC   = pc$iI_alt,
    icC_PC   = pc$cC_rep,
    icI_PC   = pc$cI_rep,
    iiC_PC   = pc$iC_rep,
    iiI_PC   = pc$iI_rep,
    std_I_rep_RT = std_I_rep,
    std_C_rep_RT = std_C_rep,
    std_I_alt_RT = std_I_alt,
    std_C_alt_RT = std_C_alt,
    Overall_Accuracy       = overall_accuracy,
    Total_Percent_Outliers = total_percent_outliers,
    row.names = NULL
  ) # builds a one-row table
}
```

```{r}
# process_subject_file: takes one subject's raw data, and returns one row of summary numbers: 
# ->    mean RT and % of correct for each of the 8 sequence cells (plus a few diagnostics)
# ->    in the context of tidyverse: read -> mutate -> filter -> group_by -> summarise --- for ONE participant 
```

# rest: only the runner function, that loops and saves the results. 