# =============================================================================
# Prime Digit Flanker: Congruency Sequence Effects Analysis
# Translated from MATLAB to R
# =============================================================================
#
# NOTE ON COLUMN LAYOUT
# ----------------------
# The original MATLAB header comment describes only 12 columns, but the code
# itself indexes up to column 17 (e.g. data(:,13), data(:,14), data(:,15),
# data(:,17)) *before* the "Warmup" column is appended. That means the raw text files actually have 16 columns, not 12 -- the comment block was out of
# date relative to the code. I've preserved the same column *positions* used
# in the MATLAB script (via the COL_* constants below) rather than guessing
# at the meaning of the columns the script never touches (8-11, 16). Please
# double-check COL_CURR_CONG / COL_PREV_CONG / COL_PREV_CONG2 / COL_RT /
# COL_ACC / COL_PREV_ACC / COL_PREV_ACC2 against your actual file if results look off.
#
# Column roles actually used by the MATLAB script (1-indexed, matching R):
#   V1  = Run label ("practice", 1-8)      <- used to strip practice trials
#   V2  = Trial number (1-96)               <- used to flag Warmup (1-4) vs Real
#   V5  = Congruency of trial N             ("Congruent"/"Incongruent")
#   V6  = Congruency of trial N-1
#   V7  = Congruency of trial N-2
#   V12 = RT
#   V13 = Accuracy of trial N               ("Correct"/"Error"/"Omission")
#   V14 = Accuracy of trial N-1
#   V15 = Accuracy of trial N-2
# (V3, V4, V8-V11, V16 exist in the file but are never referenced by the
#  original script, so they're read in but otherwise unused here too.)
#
# OUTPUT
# ------
# Writes one row per subject to
#   Prime_Digit_Flanker_Results_Lab_Exclude_Trials_1_4.txt
# with the same 23 columns as the MATLAB version:
#   SubNum, 8 trimmed-mean RTs, 8 percent-correct values, 4 trimmed RT SDs,
#   Overall_Accuracy, Total_Percent_Outliers
# =============================================================================

# ---- Column position constants (see note above) ----------------------------
```{r}
COL_RUN         <- 1
COL_TRIAL       <- 2
COL_CURR_CONG   <- 5
COL_PREV_CONG   <- 6
COL_PREV_CONG2  <- 7
COL_RT          <- 12
COL_ACC         <- 13
COL_PREV_ACC    <- 14
COL_PREV_ACC2   <- 15
```

# ---- Helper: trim values more than 3 SD from the mean (both directions) ----
```{r}
trim_3sd <- function(x) {
  m <- mean(x, na.rm = TRUE)
  s <- stats::sd(x, na.rm = TRUE)
  keep <- !is.na(x) & x >= (m - 3 * s) & x <= (m + 3 * s)
  list(
    trimmed     = x[keep],
    n_outliers  = sum(!keep, na.rm = TRUE)
  )
}
```


# ---- Helper: pull the subset of rows matching a congruency-sequence pattern
# cur/prev/prev2 are "Congruent"/"Incongruent" for trials N, N-1, N-2.
# acc_cols is a named list of which accuracy columns must equal "Correct",
# e.g. list(curr = TRUE, prev = TRUE, prev2 = TRUE) or list(prev = TRUE, prev2 = TRUE).
```{r}
get_condition <- function(df, cur, prev, prev2,
                           require_curr_correct = FALSE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE) {
  keep <- df[[COL_CURR_CONG]]  == cur  &
          df[[COL_PREV_CONG]]  == prev &
          df[[COL_PREV_CONG2]] == prev2 &
          df$Warmup == "Real"

  if (require_curr_correct)  keep <- keep & df[[COL_ACC]]       == "Correct"
  if (require_prev_correct)  keep <- keep & df[[COL_PREV_ACC]]  == "Correct"
  if (require_prev2_correct) keep <- keep & df[[COL_PREV_ACC2]] == "Correct"

  df[keep, , drop = FALSE]
}
```


# ---- Process one subject's file --------------------------------------------
```{r}
process_subject_file <- function(file_name) {

  sub_num <- as.numeric(regmatches(
    file_name,
    regexpr("(?<=Prime_Digit_Flanker_Subject_)[0-9]+", file_name, perl = TRUE)
  ))

  # Read as raw text/character columns, no header, tab-delimited
  raw <- read.delim(file_name, header = FALSE, sep = "\t",
                     colClasses = "character", quote = "\"",
                     stringsAsFactors = FALSE)

  # ---- Strip practice trials --------------------------------------------
  practice_rows <- which(raw[[COL_RUN]] == "practice")
  first_test_trial <- max(practice_rows) + 1
  data <- raw[first_test_trial:nrow(raw), , drop = FALSE]

  # ---- Flag Warmup (trials 1-4 of each block) vs Real (5-68) -------------
  data$Warmup <- ifelse(data[[COL_TRIAL]] %in% c("1", "2", "3", "4"),
                         "Warmup", "Real")

  # Numeric RT column
  data$RT <- suppressWarnings(as.numeric(data[[COL_RT]]))

  # =========================================================================
  # I. Congruency sequence effects in RT (correct trials preceded by
  #    two correct trials)
  # =========================================================================
  # "_rep" = trial N-2 was Incongruent; "_alt" = trial N-2 was Congruent
  cond_specs_I <- list(
    iI_rep = c("Incongruent", "Incongruent", "Incongruent"),
    cI_rep = c("Incongruent", "Congruent",   "Incongruent"),
    cC_rep = c("Congruent",   "Congruent",   "Incongruent"),
    iC_rep = c("Congruent",   "Incongruent", "Incongruent"),
    iI_alt = c("Incongruent", "Incongruent", "Congruent"),
    cI_alt = c("Incongruent", "Congruent",   "Congruent"),
    cC_alt = c("Congruent",   "Congruent",   "Congruent"),
    iC_alt = c("Congruent",   "Incongruent", "Congruent")
  )

  rt_trimmed <- list()
  n_outliers <- list()

  for (nm in names(cond_specs_I)) {
    spec <- cond_specs_I[[nm]]
    sub  <- get_condition(data, spec[1], spec[2], spec[3],
                           require_curr_correct = TRUE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE)
    tr <- trim_3sd(sub$RT)
    rt_trimmed[[nm]] <- tr$trimmed
    n_outliers[[nm]] <- tr$n_outliers
  }

  mean_rt <- vapply(rt_trimmed, function(x) mean(x, na.rm = TRUE), numeric(1))

  # Combined SDs across matched "rep"/"alt" x I/C groupings
  std_I_rep <- stats::sd(c(rt_trimmed$iI_rep, rt_trimmed$cI_rep), na.rm = TRUE)
  std_C_rep <- stats::sd(c(rt_trimmed$cC_rep, rt_trimmed$iC_rep), na.rm = TRUE)
  std_I_alt <- stats::sd(c(rt_trimmed$iI_alt, rt_trimmed$cI_alt), na.rm = TRUE)
  std_C_alt <- stats::sd(c(rt_trimmed$cC_alt, rt_trimmed$iC_alt), na.rm = TRUE)

  total_num_outliers   <- sum(unlist(n_outliers))
  total_percent_outliers <- total_num_outliers / nrow(data)

  # =========================================================================
  # II. Congruency sequence effects in accuracy
  #     (Method B in the original script: exclude omissions, then exclude
  #      RT outliers > 3 SD, then compute percent correct on what remains.
  #      This is the version whose numbers are actually written to file --
  #      the MATLAB "Method A", which skips the omission/outlier exclusion,
  #      is computed there too but never written out, so it's omitted here.)
  # =========================================================================
  pc <- list()

  for (nm in names(cond_specs_I)) {
    spec <- cond_specs_I[[nm]]
    sub  <- get_condition(data, spec[1], spec[2], spec[3],
                           require_curr_correct = FALSE,
                           require_prev_correct = TRUE,
                           require_prev2_correct = TRUE)

    # Exclude omissions
    sub <- sub[sub[[COL_ACC]] != "Omission", , drop = FALSE]

    # Exclude RT outliers > 3 SD from that condition's own mean
    m <- mean(sub$RT, na.rm = TRUE)
    s <- stats::sd(sub$RT, na.rm = TRUE)
    kept <- sub[!is.na(sub$RT) & sub$RT >= (m - 3 * s) & sub$RT <= (m + 3 * s), ,
                drop = FALSE]

    pc[[nm]] <- if (nro[118;1:3uw(kept) > 0) mean(kept[[COL_ACC]] == "Correct") else NA_real_
  }

  # =========================================================================
  # III. Overall accuracy (Method C): correct trials / all test trials
  # =========================================================================
  overall_accuracy <- mean(data[[COL_ACC]] == "Correct")

  # ---- Assemble this subject's output row (same column order as MATLAB) --
  data.frame(
    SubNum   = sub_num,
    ccC_RT   = mean_rt["cC_alt"],
    ccI_RT   = mean_rt["cI_alt"],
    ciC_RT   = mean_rt["iC_alt"],
    ciI_RT   = mean_rt["iI_alt"],
    icC_RT   = mean_rt["cC_rep"],
    icI_RT   = mean_rt["cI_rep"],
    iiC_RT   = mean_rt["iC_rep"],
    iiI_RT   = mean_rt["iI_rep"],
    ccC_PC   = pc$cC_alt,
    ccI_PC   = pc$cI_alt,
    ciC_PC   = pc$iC_alt,
    ciI_PC   = pc$iI_alt,
    icC_PC   = pc$cC_rep,
    icI_PC   = pc$cI_rep,
    iiC_PC   = pc$iC_rep,
    iiI_PC   = pc$iI_rep,
    std_I_rep_RT = std_I_rep,
    std_C_rep_RT = std_C_rep,
    std_I_alt_RT = std_I_alt,
    std_C_alt_RT = std_C_alt,
    Overall_Accuracy       = overall_accuracy,
    Total_Percent_Outliers = total_percent_outliers,
    row.names = NULL
  )
}
```


# =============================================================================
# Main: loop over all subject files, write combined results file
# =============================================================================
```{r}
run_all_subjects <- function(
    dir_path   = ".",
    out_file   = "Prime_Digit_Flanker_Results_Lab_Exclude_Trials_1_4.txt"
) {
  files <- list.files(dir_path,
                       pattern = "^Prime_Digit_Flanker_Subject_.*\\.txt$",
                       full.names = TRUE)

  if (length(files) == 0) {
    stop("No files matching 'Prime_Digit_Flanker_Subject_*.txt' found in ", dir_path)
  }

  # Delete any pre-existing results file, matching the MATLAB script's behavior
  out_path <- file.path(dir_path, out_file)
  if (file.exists(out_path)) file.remove(out_path)

  results <- do.call(rbind, lapply(files, process_subject_file))

  # Header block matching the MATLAB output format
  header_lines <- c(
    "Experiment ID\t Prime_Digit_Flanker_Results",
    "The data from each subject appear on a different row",
    "Data come from the following conditions",
    "",
    "Overall Analysis",
    "\tRT\t\t\t\t\t\t\t\t PC\t\t\t\t\t\t\t\t Stdev\t\t\t\t Overall_Accuracy",
    paste(
      "SubNum", "ccC_RT", "ccI_RT", "ciC_RT", "ciI_RT",
      "icC_RT", "icI_RT", "iiC_RT", "iiI_RT",
      "ccC_PC", "ccI_PC", "ciC_PC", "ciI_PC",
      "icC_PC", "icI_PC", "iiC_PC", "iiI_PC",
      "std_I_rep_RT", "std_C_rep_RT", "std_I_alt_RT", "std_C_alt_RT",
      "Overall_Accuracy", "Total_Percent_Outliers",
      sep = "\t"
    )
  )

  con <- file(out_path, open = "w")
  writeLines(header_lines, con)
  close(con)

  write.table(results, out_path, sep = "\t", row.names = FALSE, col.names = FALSE,
              append = TRUE, quote = FALSE)

  invisible(results)
}
```


# Example usage:
# results <- run_all_subjects(dir_path = "path/to/your/data")
